---
title: "Data Science I Homework 5 - lzs2109"
author: "Louis Sharp"
date: "11/11/2021"
output: github_document
---

```{r}
library(tidyverse)
```


### **Problem 1**

```{r}
homicide_df = read_csv("./data/homicide-data.csv") %>% 
  mutate(city_state = str_c(city, state, sep = ", "),
         status = ifelse(disposition == "Closed by arrest", "solved", "unsolved"))
```

The raw data from homicide-data.csv contains the variables `r names(homicide_df)`, which give ID numbers to each homicide, in addition to the date, victim's information, the location (city, state, and specific latitude/longitude) of the homicide, and finally the status of the case (closed/open/arrest/no arrest). There are 51 cities and a total of `r nrow(homicide_df)` homicides with data included in the dataset.

```{r}
homicide_df %>% 
  group_by(city_state, status) %>% 
  count()

bmore = 
  homicide_df %>%
    filter(city_state == "Baltimore, MD") %>%
    group_by(status) %>% 
    count()
bmore = prop.test(x = bmore$n[2], n = bmore$n[1] + bmore$n[2])
bmore %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high)
```

```{r}
unsolved_murders = function(location) {
  
  city = homicide_df %>% 
           filter(city_state == location) %>%
           group_by(status) %>% 
           count()
  
  city = prop.test(x = city$n[2], n = city$n[1] + city$n[2])
  
  city %>% 
    broom::tidy() %>% 
    select(estimate, conf.low, conf.high)
  
}

unsolved_murders("Atlanta, GA")
```

```{r}
homicide_df %>% 
  group_by(city_state, status) %>% 
  count()
```


## Problem 2

```{r, message = F, warning = F}
hw5_df = 
  tibble(
  filenames = list.files("data/hw5_data/"),
  location = str_c("./data/hw5_data/", filenames),
  data = map(location, read_csv)
) %>% 
  mutate(filenames = str_remove(filenames, ".csv$")) %>% 
  rename(treatment = filenames) %>% 
  unnest() %>% 
  pivot_longer(week_1:week_8, 
               names_to = "week", 
               names_prefix = "week_", 
               values_to = "data_value") %>% 
  mutate(week = as.numeric(week),
         group = ifelse(str_detect(treatment, "^con"), "control", "treatment"),
         subject_id = str_remove(treatment, "^con_"),
         subject_id = str_remove(subject_id, "^exp_")) %>% 
  select(treatment, subject_id, group, week, data_value)
  

hw5_df %>% 
  ggplot(aes(x = week, y = data_value, color = group)) +
  geom_line(aes(group = treatment), alpha = 0.6)
```

Based on the spaghetti plot, we can see that by the end of week 8, all subjects in the control arm have a lower data value than all subjects in the treatment group. If the treatment was meant to increase the data value, it appears to be effective in all subjects, including those that had lower starting data values than subjects in the control group.


## Problem 3

